Supplement

### 2023-03-30 06_Paper/ER-ED/ERED_Stage2/Supplement.Rmd
added reasons for choice
post hoc contrasts view

``` {r TabNV, echo=FALSE, message=FALSE, warning=FALSE}

papaja::apa_table(
  df.NV.subj,
  caption = "Results of Shapiro-Wilk test for normal distribution of subjective arousal and effort ratings for all strategies.",
  escape = FALSE,
  placement = "H")

papaja::apa_table(
  df.NV.EMG,
  caption = "Results of Shapiro-Wilk test for normal distribution of Corrugator and Levator activity for all strategies.",
  escape = FALSE,
  placement = "H")

@@

## Post-hoc tests of strategies for effects of ER on subjective arousal and physiological responding {#SupplementEffectER}

``` {r SupplEffectER, echo=FALSE, message=FALSE, warning=FALSE} 
papaja::apa_table(
  SubjArousalReg_con,
  caption = "Post-hoc tests for effects of ER strategies on subjective arousal ratings.",
  escape = FALSE,
  placement = "H"
  )

papaja::apa_table(
  EMGCorrReg_con,
  caption = "Post-hoc tests for effects of ER strategies on Corrugator activity",
  escape = FALSE,
  placement = "H"
  )

papaja::apa_table(
  EMGLevReg_con,
  caption = "Post-hoc tests for effects of ER strategies on Levator activity",
  escape = FALSE,
  placement = "H"
  )

@@

>>>>

``` {r TabNVRatings, echo=FALSE, message=FALSE, warning=FALSE}

papaja::apa_table(
  df.NV.subj,
  caption = "Results of Shapiro-Wilk test for normal distribution of subjective arousal and effort ratings for all strategies.",
  escape = FALSE,
  placement = "H") 
```

```{r TabNCEMG}
papaja::apa_table(
  df.NV.EMG,
  caption = "Results of Shapiro-Wilk test for normal distribution of Corrugator and Levator activity for all strategies.",
  escape = FALSE,
  placement = "H")

@@

## Post-hoc contrasts for effects of valence on subjective arousal and physiological responding {#SupplementEffectValence}

``` {r SupplEffectArousalView, echo=FALSE, message=FALSE, warning=FALSE} 
papaja::apa_table(
  SubjArousalView_con,
  caption = "Post-hoc contrasts for effects of valence on subjective arousal ratings in the active viewing conditions.",
  escape = FALSE,
  placement = "H",
  font_size = "footnotesize"
  )
```

``` {r SupplFigArousalView, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective arousal ratings of the active viewing conditions vizalized as boxplots. Dots represent individual effort ratings placed in 150 quantiles.", fig.pos="H"}
knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "FigSubjArousalView.png"))
```

``` {r SupplEffectCorrView, echo=FALSE, message=FALSE, warning=FALSE}
papaja::apa_table(
  EMGCorrView_con,
  caption = "Post-hoc contrasts for effects of valence on Corrugator activity in the active viewing conditions.",
  escape = FALSE,
  placement = "H",
  font_size = "footnotesize"
  )
```

``` {r SupplFigCorrView, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Corrugator activity in mV during the active viewing conditions, vizalized as boxplots. Dots represent individual Corrugator activity measures placed in 150 quantiles.", fig.pos="H"}
knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "FigCorrView.png"))
```

``` {r SupplEffectLevView, echo=FALSE, message=FALSE, warning=FALSE}
papaja::apa_table(
  EMGLevView_con,
  caption = "Post-hoc contrasts for effects of valence on Levator activity in the active viewing conditions.",
  escape = FALSE,
  placement = "H",
  font_size = "footnotesize"
  )
```

``` {r SupplFigLevView, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Levator activity in mV during the active viewing conditions, vizalized as boxplots. Dots represent individual Levator activity measures placed in 150 quantiles.", fig.pos="H"}
knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "FigLevView.png"))
```

## Post-hoc contrasts for effects of ER strategies on subjective arousal and physiological responding {#SupplementEffectER}

``` {r SupplEffectArousalReg, echo=FALSE, message=FALSE, warning=FALSE} 
papaja::apa_table(
  SubjArousalReg_con,
  caption = "Post-hoc contrasts for effects of ER strategies on subjective arousal ratings.",
  escape = FALSE,
  placement = "H",
  font_size = "footnotesize"
  )
```

``` {r SupplFigArousalReg, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective arousal ratings vizalized as boxplots. Dots represent individual effort ratings placed in 150 quantiles.", fig.pos="H"}
knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "FigSubjArousalReg.png"))
```

``` {r SupplEffectCorrReg, echo=FALSE, message=FALSE, warning=FALSE}
papaja::apa_table(
  EMGCorrReg_con,
  caption = "Post-hoc contrasts for effects of ER strategies on Corrugator activity",
  escape = FALSE,
  placement = "H",
  font_size = "footnotesize"
  )
```

``` {r SupplFigCorrReg, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Corrugator activity in mV vizalized as boxplots. Dots represent individual Levatorr activity measures placed in 150 quantiles.", fig.pos="H"}
knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "FigCorrReg.png"))
```

``` {r SupplEffectLevReg, echo=FALSE, message=FALSE, warning=FALSE}
papaja::apa_table(
  EMGLevReg_con,
  caption = "Post-hoc contrasts for effects of ER strategies on Levator activity",
  escape = FALSE,
  placement = "H",
  font_size = "footnotesize"
  )

@@

``` {r SupplFigLevReg, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Levator activity in mV vizalized as boxplots. Dots represent individual Levator activity measures placed in 150 quantiles.", fig.pos="H"}
knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "FigLevReg.png"))
```
\newpage

## Reasons for decision made by the participants in the last regulation block
